\pkg{SVMBridge}: Using SVM Solvers from R

### 2015-09-15 paper/article.tex
small update

@@

@@

@@

@@

>>>>

\subsection{Reading Sparse Data}

Most SVM solver work with the sparse data format.
This format consists of:
Each line (delimited by a CR/LF) is given by a label
and the non-zero components of the data point,
e.g. to encode the vector six dimensional vector 
$0 0 0 0.2 0 1.4$ belonging to class $3$, the sparse 
data format would contain the line {3 4:0.2 6:1.4}.

Although reading these files into R is possible via either
the kernlab or the e1071 routines, both only provide R solutions,
and therefore suffer from suboptimal performance.
The SVMBridge package provides a simple sparse data format 
reading and writing, which are implemented in C++ and
therefore are nearly two orders of magnitudes faster than
the corresponding e1071 routines.
Notice, that currently only dense matrices are supported,
TODO: work around this with the Sparse Matrix Package.

@@

Multiclass is supported, where possible.
Note that several SVM packages only support binary problems.
In these cases, training a one-vs-all machine is rather easy, if the
data is loaded into R first.

Reading a model is possible via the \code{readModelFromFile ()} function.
This will try to detect the format of the file by calling the 
\code{isModelFile} routine of each known wrapper.
Unluckily, several SVM solver use similar model formats, so that
a direct detection is not possible, e.g. CVM/BVM follow the LIBSVM
format, but add a comment (with '\#')about the running time to the
bottom of the model file. Apart from this change, there is no difference.
From a practical viewpoint we extended the LIBSVM model reader
to cope with this extra line, so that there is no need for an extra CVM/BVM reader.
This means that reading a CVM model will make the SVMBridge to detect a LIBSVM
model (if the LIBSVM wrapper is loaded).
In these cases, if multiple models claims ownership, a "default" model can be provided,
which will take precedence over other models. Without a default,
the model will be random.

@@

Predicting from a trained model is rather easy, as there are usually not many options.
As with training, the predict routine will accept a model either in memory or from a file.

@@

\subsection{Helper Routines}

...

@@

We acknowledge support by the Mercator Research Center Ruhr,
under grant Pr-2013-0015 \textit{Support-Vektor-Maschinen f{\"u}r extrem gro{\ss}e Datenmengen} and
partial support by the German Research Foundation (DFG) within the Collaborative Research Centers SFB 823
\textit{Statistical modelling of nonlinear dynamic processes}, Project C2.
